---
title: 'Assignment 8: Simulation and Probability Distribution'
author: "Anamul Haque"
date: "29/2/2020"
output:
  html_document:
    theme : united
    highlight: tango
    toc: true
    toc_float : true
---

## Q1. Finding the probability that a normal random variable with mean 22 and variance 25 lies between 16.2 and 27.5

```{r}
# Variance is 25, therefore sd = sqrt(25) = 5
# Mean is 22
# Probability that the normal variable will be less than 16.2
# Probability of a random variable x in normal distribution pnorm(x, mean, sd)
p1 = pnorm(16.2,22,5)
# Probability that the normal variable will be less than 27.5
p2 = pnorm(27.5,22,5)

#  Probability that the normal random variable lies between 16.2 and 27.5
pq1 = p2 - p1
pq1
```

## Q2. Finding the probability that a normal random variable with mean 25 and and standard deviation 3 is greater than 27
```{r}
# Here mean is 25 and sd is 3 
# Probability that the normal variable will be less than 27
# Probability of a random variable x in normal distribution pnorm(x, mean, sd)
q = pnorm(27,25,3)

# Probability that the normal variable will be greter than 27
pq2 = 1- q
pq2
```
## Q3. Finding the probability that in 60 tosses of a fair coin (probability 0.5) the head comes up between 20 and 30 times. The coin toss is a binomial distribution 

```{r}
# Here the probability is 0.5 
# Probability of an expected outocomr x in binomial distribution pbinom(expected_outcome, total_outcome, probability)
# Probability of getting 30 heads from 60 toss 
p30 = pbinom(30, 60, 0.5)
# Probability of getting 30 heads from 60 toss 
p20 = pbinom(20, 60, 0.5)

# Probability of getting head between 20 and 30 times
pq3 = p30 - p20
pq3
```

## Q4. A random variable X has Poisson distribution with mean 7. Finding the probability that X is strictly greater than 10

```{r}
# Here the mean is 7
# Probability of getting random vraible X is strictly less than 10 is
q4 = ppois(10,7)

# Probability of getting random vraible X is strictly greater than 10 is
pq4 = 1-q4
pq4
```

## Q5. Generating 500 samples from Student's t distribution with 5 degrees of freedom and plotting them in the histogram

```{r}
# To generate 500 samples in the students t distribution we have to use the formula rt(n, df, ncp). Here n is the number of observation, df is the degree of freedom and ncp is the non-centrality parameter. I am omiitting ncp here, since I am using the central t distribution.   
td <- rt(500, 5)
td
# Plottting the distribution in the histogram
hist(td,40)
```

## Q6. Plotting the probability mass function for the Poisson distribution with mean 4.5 and 12 respectively.  

```{r}
# Without no upper limit 
x <- 0:25
plot(x, dpois(x, lambda = 4.5), main = "Probability Mass Function for lambda 4.5")
plot(x, dpois(x, lambda = 12), main = "Probability Mass Function for lambda 12")
```


